\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Title of the Thesis}

\author{Sourabh Bharti}
\rollnum{2011-AN11}
%\otherdegrees{B.A., North Dakota State University, 2005 \\
%	      M.S., University of Reno, 2007}

\degree{\textbf{Master of Technology}\\ in}		%  #1 {long descr.}
	{\textbf{Advanced Networks}}		%  #2 {short descr.}

\dept{\textbf{Advanced Networks}}			%  #1 {designation}
	{}	
		%  #2 {name}
%\vspace{0.7in}

%\vspace{0.8in}

\advisor{Prof./Dr.}				%  #1 {title}
	{Supervisor and Prof./Dr. Co-Supervisor}		%  #2 {name}
	


%\reader{Prof.~Rachel Goddard}		%  2nd person to sign thesis
%\readerThree{Ms.~Thora Nea}		%  3rd person to sign thesis


\abstract{
	}

\declaration[Candidate's Declaration]{I hereby certify that I have properly checked and verified all the items as prescribed
in the check-list and ensure that my thesis is in the prop er format as specified in the
guideline for thesis preparation. \\ I declare that the work containing in this rep ort is my own work. I understand that
plagiarism is defined as any one or combination of the following: \begin{enumerate}
	\item To steal and pass off (the ideas or words of another) as one's own
	\item To use (another's production) without crediting the source
	\item To commit literary theft
	\item To present as new and original idea or product derived from an existing source.
\end{enumerate}
I understand that plagiarism involves an intentional act by the plagiarist of using someone else's work/ideas completely/partially and claiming authorship/originality of the work/ideas. Verbatim copy as well as close resemblance to some else's work constitute plagiarism. \\  I have given due credit to the original authors/sources for all the words, ideas, diagrams,
graphics, computer programmes, experiments, results, websites, that are not my original contribution. I have used quotation marks to identify verbatim sentences and given
credit to the original authors/sources. \\ I affirm that no portion of my work is plagiarized, and the experiments and results
reported in the report/dissertation/thesis are not manipulated. In the event of a complaint of plagiarism and the manipulation of the experiments and results, I shall be fully
responsible and answerable. My faculty supervisor(s) will not be responsible for the
same. \\\\
Signature: \\ \\
Name: \\ \\
Roll. No: \\ \\
Date: 


}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
	Here's where you acknowledge people who helped.
	But keep it short, i.e., no more than one page.
	}

% \IRBprotocol{E927F29.001X}	% optional!

\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex
\input chapter1.tex
\input chapter2.tex
\input chapter3.tex
\input chapter4.tex
\input chapter5.tex


%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{plain}	% or "siam", or "alpha", etc.
\nocite{*}		% list all refs in database, cited or not
\bibliography{refs}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
\appendix
\input appendixA.tex
\input appendixB.tex


\end{document}

